---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(targets)
```

# Phenocam Forecast for NEFI summer course 2022

<!-- badges: start -->
<!-- badges: end -->

Team:

- [Eric Scott](https://github.com/Aariq)
- [Yiluan Song](https://github.com/yiluansong)
- [Ross Alexander](https://github.com/alexanderm10)
- [Jussi Mäkinen](https://github.com/jusmak)


# Literature 

- https://www.sciencedirect.com/science/article/abs/pii/S0034425720303266

# Data exploration

[Data exploration](docs/EDA.md)

## Timeseries

```{r}
tar_read(ts_plot)
```


# Model structure

Data model
$$GCC_{t, s} \sim N (X_{t, s}, \tau_{o, GCC})$$
$$EVI_{t, s} \sim N (X_{t, s}, \tau_{o, EVI})$$

Process model
$$X_{t, s} \sim N(X_{t-1, s}+ \beta_{s} T_{t, s} + \mu_{s},\tau_{a})$$
$$X_{t, s} \sim N(X_{t-1, s}+ \beta T_{t, s},\tau_{a})$$
$$X_{t, s} \sim N(X_{t-1, s},\tau_{a})$$

Priors
$$X_{1, s} \sim N (mu_{IC, s}, \tau_{IC, s})$$
$$\tau_{o, GCC} \sim Gamma(a_{o, GCC},r_{o, GCC})$$
$$\tau_{o, EVI} \sim Gamma(a_{o, EVI},r_{o, EVI})$$
$$\tau_{a} \sim Gamma(a_a,r_a)$$

### JAGS code:

```{r echo=FALSE, render='asis', comment=''}
cat(tar_read(RandomWalk))
```



# Forecasts

Some examples

- [2020-11-24](https://github.com/Aariq/efi-2022-phenocam/blob/main/forecasts/2020-11-24/plot.pdf)
- [2021-07-22](https://github.com/Aariq/efi-2022-phenocam/blob/main/forecasts/2021-07-22/plot.pdf)
- [2022-05-18](https://github.com/Aariq/efi-2022-phenocam/blob/main/forecasts/2022-05-18/plot.pdf)


### Workflow:

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
cat(
  "```mermaid",
  targets::tar_mermaid(targets_only = TRUE, reporter = "silent"),
  "```",
  sep = "\n"
)
#this should display correctly on GitHub, or code can be pasted into https://mermaid.live
```


# Resources for Challenge

- [challenge docs](https://projects.ecoforecast.org/neon4cast-docs/theme-phenology.html)
- [phenocam](https://phenocam.sr.unh.edu/webcam/)


gcc data is here:

```r
gcc_dat <- 
  readr::read_csv(
    "https://data.ecoforecast.org/targets/phenology/phenology-targets.csv.gz",
    guess_max = 1e6
  )

```

site metadata is here:

```r
site_data <- 
  readr::read_csv(
    "https://raw.githubusercontent.com/eco4cast/neon4cast-phenology/master/Phenology_NEON_Field_Site_Metadata_20210928.csv"
    )

```


# Repo structure

- `data/` put raw data here
- `R/` put R functions to be `source()`ed here
- `docs/` put .Rmd files to be rendered here
